Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-05-08 sections/4gluing_alt.tex

\begin{proof}
    Using \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} we will argue in terms of algebras over $\infty$-operads. Since the formation of algebras is contravariantly functorial (as precomposition), it is sufficient to show that there is an equivalence of $\infty$-operads
    %
    \begin{equation}
        \mathsf{colim}_{i \geq 0} \disk_{/M_i} \xrightarrow{\ \ \simeq \ \ } \disk_{M},
    \end{equation}
    %
    as well as the same for $\disk[r]_{/M}$. In the case of the former, as originally noted in the proof of \cite[cor.2.40]{aft_fhstrat}, the result follows from using \cite[cor.1.6.]{dugger2004hypercovers}, an argument about configuration spaces, as well as \cite[lem.2.21]{aft_fhstrat}, which explains the relation of these to the above operad. In the case of the latter, the situation is even simpler because of its discrete nature. One way to show this is to notice that the functor from the ordinary, nonhomtopy colimit factors through $\mathsf{colim}_{i \geq 0} \disk[r]_{/M_i} \xrightarrow{} \disk[r]_{/M}$, in which case it suffices to find an equivalence of \emph{ordinary} categories
    %
    \begin{equation}
        \mathsf{colim}_{i \geq 0} \disk[r]_{/M_i} \xrightarrow{} \disk[r]_{/M},
    \end{equation}
    %
    where the colimit is now the one relevant to ordinary category theory, namely the nonhomotopy one. But it's now easy to see that this the canonical morphism above is an equivalence since for every $U \in \disk_{/M}$ there will be a finite integer $i$, such that $U \subset M_i$.
\end{proof}

>>>>

\begin{proof}
    Using \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} we will argue in terms of algebras over $\infty$-operads. Since the formation of algebras is contravariantly functorial (as precomposition), it is sufficient to show that there is an equivalence of $\infty$-operads
    %
    \begin{equation}
        \mathsf{colim}_{i \geq 0} \disk_{/M_i} \xrightarrow{\ \ \simeq \ \ } \disk_{M},
    \end{equation}
    %
    as well as the same for $\disk[r]_{/M}$. In the case of the former, as originally noted in the proof of \cite[cor.2.40]{aft_fhstrat}, the result follows from using \cite[cor.1.6.]{dugger2004hypercovers}, an argument about configuration spaces, as well as \cite[lem.2.21]{aft_fhstrat}, which explains the relation of these to the above operad. %In the case of the latter, the situation is even simpler because of its discrete nature. One way to show this is to notice that the functor from the ordinary, nonhomtopy colimit factors through $\mathsf{colim}_{i \geq 0} \disk[r]_{/M_i} \xrightarrow{} \disk[r]_{/M}$, in which case it suffices to find an equivalence of \emph{ordinary} categories
    %
    %\begin{equation}
    %    \mathsf{colim}_{i \geq 0} \disk[r]_{/M_i} \xrightarrow{} \disk[r]_{/M},
    %\end{equation}
    %
    %where the colimit is now the one relevant to ordinary category theory, namely the nonhomotopy one. But it's now easy to see that this the canonical morphism above is an equivalence since for every $U \in \disk_{/M}$ there will be a finite integer $i$, such that $U \subset M_i$.
\end{proof}
